### 2012-05-17 GUIErrorDetector/paper/introduction.tex
tweak space

\makeatletter
\newenvironment{myquotation}
               {\list{}{\listparindent=0pt%whatever you need
                        \itemindent    \listparindent
                        \leftmargin=10pt%  whatever you need
                        \rightmargin=0pt%whatever you need
                        \topsep=0pt%%%%%  whatever you need
                        \parsep        \z@ \@plus\p@}%
                \item\relax}
               {\endlist}
\makeatother

\begin{myquotation}
All GUI objects, including visual components and data models, must be
 accessed exclusively from the \textit{event dispatching thread}.
\end{myquotation}

@@

Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
Invalid thread access is one of the top 3 bugs in developing a SWT application, and is
the source of many concurrency bugs~\cite{top3bugs}.
A Google search for ``SWTException:Invalid thread access''  returns over 11,800 hits,
consisting of numerous bug reports, forum posts, and mailing list threads on
this problem. Eclipse, the IDE for Java development, is built on top of SWT\@.
Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
and discussion forum returns 2732 bug reports and 351 distinct discussion threads, respectively. 
We manually studied all 156 distinct \textit{confirmed} bug reports, and 
found this error has been confirmed in at least 20 distinct Eclipse projects
and 40 distinct Eclipse components. Even after over 10 years of active development,
a recent release of Eclipse still contains this error (bug id: 333533, reported in January 2011).
 In addition, the invalid thread access error
is severe. It is user-perceivable, it cannot be recovered by the program itself,
and it often terminates the whole application. In many circumstances as described in the bug reports,
users must restart the application to recover from the error.
Furthermore, many reported  errors are non-trivial to diagnose and fix.
Developers usually need non-local reasoning to find the specific
UI interactions that can trigger the bug;  it took developers 2 years
to fix Eclipse bug 51757 and verify the patch.

\begin{figure}[t]
\hspace{6mm}{In class: org.mozilla.gecko.gfx.LayerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
68.  public LayerView(Context context, LayerController controller) \ttlcb
69.     super(context);
        ....
73.     mRenderer = new LayerRenderer(this);
74.     setRenderer(mRenderer);
        ...
     \ttrcb
\end{alltt}
\end{CodeOut}
\hspace{6mm} {In Android library class: android.opengl.GLSurfaceView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
272. public void setRenderer(Renderer renderer) \ttlcb
        ...
282.    mGLThread = new GLThread(renderer);
283.    mGLThread.start();   
     \ttrcb
\end{alltt}
\end{CodeOut}
 \hspace{6mm}{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
221.    gl.glViewport(0, 0, width, height);
222.    mView.setViewportSize(new IntSize(width, height));
     \ttrcb
\end{alltt}
\end{CodeOut}
\tinystep
\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
calls method \CodeIn{setRenderer} which 
spawns a new thread on line 283. This newly created, non-UI thread calls back method
\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222 of \CodeIn{LayerRenderer},
causing an invalid thread access error. Our tool
finds this error and generates a report as shown in
Figure~\ref{fig:report}.
}} \vspace{-1.8mm}
\end{figure}

>>>>

\makeatletter
\newenvironment{myquotation}
               {\list{}{\listparindent=0pt%whatever you need
                        \itemindent    \listparindent
                        \leftmargin=14pt%  whatever you need
                        \rightmargin=14pt%whatever you need
                        \topsep=0pt%%%%%  whatever you need
                        \parsep        \z@ \@plus\p@}%
                \item\relax}
               {\endlist}
\makeatother

%\begin{myquotation}
%this is on purpose. if not, the code in the next page will be
%scattered into 2 pages
\vspace{-2mm}
\begin{quotation}
All GUI objects, including visual components and data models, must be
 accessed exclusively from the \textit{event dispatching thread}.
\end{quotation}
\vspace{-2mm}
%\end{myquotation}

@@

Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
Invalid thread access is one of the top 3 bugs in developing a SWT application, and is
the source of many concurrency bugs~\cite{top3bugs}.
A Google search for ``SWTException:Invalid thread access''  returns over 11,800 hits,
consisting of numerous bug reports, forum posts, and mailing list threads on
this problem. Eclipse, the IDE for Java development, is built on top of SWT\@.
Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
and discussion forum returns over 2700 bug reports and 350 distinct discussion threads, respectively. 
We manually studied all 156 distinct \textit{confirmed} bug reports, and 
found this error has been confirmed in at least 20 distinct Eclipse projects
and 40 distinct Eclipse components. Even after over 10 years of active development,
a recent release of Eclipse still contains this error (bug id: 333533, reported in January 2011).
 In addition, the invalid thread access error
is severe. It is user-perceivable, it cannot be recovered by the program itself,
and it often terminates the whole application. In many circumstances as described in the bug reports,
users must restart the application to recover from the error.
Furthermore, many reported  errors are non-trivial to diagnose and fix.
Developers usually need non-local reasoning to find the specific
UI interactions that can trigger the bug;  it took developers 2 years
to fix Eclipse bug 51757 and verify the patch.

\begin{figure}[t]
\hspace{6mm}{In class: org.mozilla.gecko.gfx.LayerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
68.  public LayerView(Context context, LayerController controller) \ttlcb
69.     super(context);
        ....
73.     mRenderer = new LayerRenderer(this);
74.     setRenderer(mRenderer);
        ...
     \ttrcb
\end{alltt}
\end{CodeOut}
\hspace{6mm} {In Android library class: android.opengl.GLSurfaceView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
272. public void setRenderer(Renderer renderer) \ttlcb
        ...
282.    mGLThread = new GLThread(renderer);
283.    mGLThread.start();   
     \ttrcb
\end{alltt}
\end{CodeOut}
 \hspace{6mm}{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
221.    gl.glViewport(0, 0, width, height);
222.    mView.setViewportSize(new IntSize(width, height));
     \ttrcb
\end{alltt}
\end{CodeOut}
\tinystep
\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
revision d7fa4814218d. On line 74, \CodeIn{LayerView}'s constructor
calls method \CodeIn{setRenderer} which 
spawns a new thread on line 283. This newly created, non-UI thread calls back method
\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222 of \CodeIn{LayerRenderer},
causing an invalid thread access error. Our tool
finds this error and generates a report as shown in
Figure~\ref{fig:report}.
}} %\vspace{-1.8mm}
\end{figure}
